crul
====

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

An HTTP client, with perhaps the main goal being to hook into 
[webmockr](https://github.com/ropenscilabs/webmockr) for flexible and easy 
http request caching, and eventually into 
[vcr](https://github.com/ropenscilabs/vcr) for another approach to http 
request caching.

## Installation

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("ropenscilabs/crul")
```

```{r}
library("crul")
```

## the client

`HttpClient` is where to start

```{r}
(x <- HttpClient$new(url = "https://httpbin.org"))
```

Makes a R6 class, that has all the bits and bobs you'd expect for doing HTTP 
requests. When it prints, it gives any defaults you've set. As you update 
the object you can see what's been set

```{r}

```



## Meta

* Please [report any issues or bugs](https://github.com/ropenscilabs/crul/issues).
* License: MIT
* Get citation information for `crul` in R doing `citation(package = 'crul')`
* Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
