---
title: "API package best practices"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{5. API package best practices}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Importing crul

In most cases you'll only need to import one thing from `crul`: 
`HttpClient`. Add crul to `Imports` in your `DESCRIPTION` file,
and ad an entry like `@importFrom crul HttpClient` somewhere in 
your package documentation, for example:

```r
#' Some function
#' 
#' @export
#' @importFrom crul HttpClient
#' ...
```

## HTTP request function

If you have more than one function that needs to make an HTTP request
it's probably useful to have a function for doing HTTP requests. The
following is an example of a function.

```{r eval=FALSE}
xGET <- function(url, path, args = list(), ...) {
  cli <- crul::HttpClient$new(url, opts = list(...))
  res <- cli$get(path = path, query = args)
  res$raise_for_status()
  res$parse("UTF-8")
}
```

There's some features to note in the above function:

* `url`: this really depends on your setup. In some cases the base URL 
doesn't change, so you can remove the `url` parameter and define the 
url in the `crul::HttpClient$new()` call. 
* `path`: this likely will hold anything after the base path
* `args`: named list of query arguments. the default of `list()` 
means you can then use the function and not have to pass `args` 
in cases where no query args are needed.
* `...`: it's called an ellipsis. see example and discussion below.

You can use the function like:

```{r eval=FALSE}
x <- xGET("https://httpbin.org", "get", args = list(foo = "bar"))
# parse the JSON to a list
jsonlite::fromJSON(x)
# more parsing
```

Because we used an ellipsis, anyone can pass in curl options like:

```{r eval=FALSE}
xGET("https://xxx.org", args = list(foo = "bar"), verbose = TRUE)
```

Curl options are important for digging into the details of HTTP 
requests, and go a long way towards users being able to sort out 
their own problems, and help you diagnose problems as well.

Alternatively, you can just do the HTTP request in your `xGET` function
and return the response object - and line by line, or with 
another function, parse results as needed.

## Failing with fauxpas

coming soon ...

## Mocking with webmockr

[webmockr][] is a package for stubbing and setting expectations on 
HTTP requests. It has support for working with two HTTP request 
packages: [crul][] and [httr][]. 

There are a variety of use cases for `webmockr`. 

* Use it in an interactive R session where you're working 
on a project and want to mock HTTP requests and set certain responses. 
* You can be on a plane and still allow requests to work without an 
internet connection by setting a response to give back. 
* Test hard to test scenarios in your code or package. `webmockr` 
allows you to give back exact responses just as you describe and 
even fail with certain HTTP conditions. Getting certain failures 
to happen with a remote server can sometimes be difficult. 
* Package test suite: you can use `webmockr` in a test suite, 
although the next section covers `vcr` which builds on top of 
`webmockr` and is ideal for tests.


## Testing with vcr

[vcr][] records and replays HTTP requests. It's main use case is for 
caching HTTP requests in test suites in R packages. It has support 
for working with two HTTP request packages: [crul][] and [httr][]. 

To use `vcr` for testing the setup is pretty easy. 

1. Add `vcr` to Suggests in your DESCRIPTION file
2. Make a file in your `tests/testthat/` directory called 
`helper-yourpackage.R` (or skip if as similar file already exists). 
In that file use the following lines to setup your path for storing 
cassettes (change path to whatever you want):

```r
library("vcr")
invisible(vcr::vcr_configure())
```

3. In your tests, for whichever tests you want to use `vcr`, wrap 
the tests in a `vcr::use_cassette()` call like:

```r
library(testthat)
test_that("my test", {
  vcr::use_cassette("rl_citation", {
    aa <- rl_citation()

    expect_is(aa, "character")
    expect_match(aa, "IUCN")
    expect_match(aa, "www.iucnredlist.org")
  })
})
```

That's it! Just run your tests are you normally would and any HTTP 
requests done by `crul` or `httr` will be cached on the first test run
then the cached responses used every time thereafter. 


## What else?

Let us know if there's anything else you'd like to see in this 
document and/or if there's anything that can be explained better.


[crul]: https://github.com/ropensci/crul
[webmockr]: https://github.com/ropensci/webmockr
[vcr]: https://github.com/ropensci/vcr
[httr]: https://github.com/r-lib/httr
